QPLIB: A Library of Quadratic Programming Instances

### 2017-02-01 methods.tex
addded citations to commonly-used non-GAMS continuous QP solvers

The solvers in Table \ref{t:solvers} which implement incomplete methods for continuous NLPs (a problem class containing QCQ) are \conopt, \ipopt, \minos, \snopt, and \knitro. Note that all these solvers tackle the more general class of continuous NLP, while we use them only for the considerably more restricted class of QP. While there are many different approaches for continuous NLPs in general, we therefore describe here on those that are particularly well-suited for QP, i.e.:
%
\begin{itemize}
 \item active set methods (\conopt, \minos, \snopt, \knitro) \cite{Dost09};
 %
 \item interior point methods (\ipopt, \knitro) \cite{Wright97};
 %
 \item projected gradient methods \cite{CalaMore87:mp,ChenGui13:coap}.
\end{itemize}
%
Active set and interior point methods have been defined for *C* but also for general (continuous) NLPs. In fact, all of the solvers named above target this larger problem class.

@@

\paragraph{Projected gradient methods.}
%
These approaches are similar to active-set methods in that at each iteration they consider the gradient projected onto the set of active constraints, in order to (try to) guarantee feasibility of the next iterate. They differ from active-set methods in that the set of active constraints can change dramatically on each iteration, and they have stronger convergence properties, more akin to those of interior-point methods.

>>>>

The solvers in Table \ref{t:solvers} which implement incomplete methods for continuous NLPs (a problem class containing QCQ) are \conopt, \ipopt, \minos, \snopt, and \knitro. Note that all these solvers tackle the more general class of continuous NLP, while we use them only for the considerably more restricted class of QP. Aside from solvers provided by GAMS, there are a number of other, specialized incomplete QP solvers, such as
\cqp \cite{GoulOrbaRobi13:mpc},
\dqp \cite{GoulRobi16:coap} and
\ooqp \cite{GertWrig03:toms}
for convex problems, and
\bqpd \cite{Flet:2000},
\qpa \cite{GoulToin02i} and
\qpb \cite{ConnGoulOrbaToin:2000},
\qpc \cite{GoulOrbaToin03:toms},
\sqic \cite{Gill2015}
for nonconvex ones
While there are many different approaches for continuous NLPs in general, we mention here those that are particularly well-suited for QP, i.e.:
%
\begin{itemize}
 \item active set methods (\conopt, \minos, \snopt, \knitro, \bqpd, \qpa, \sqic) \cite{Dost09};
 %
 \item interior point methods (\ipopt, \knitro, \cqp, \ooqp, \qpb, \qpc) \cite{Wright97};
 %
 \item projected gradient methods (\dqp) \cite{CalaMore87:mp,ChenGui13:coap}.
\end{itemize}
%
Active set and interior point methods have been defined for *C* but also for general (continuous) NLPs, and many of the solvers named above target this
larger problem class.

@@

\paragraph{Projected gradient methods.}
%
These approaches are similar to active-set methods in that at each iteration they project the steepest descent direction onto the constraint set in order to (try to) predict the optimal active set; the predicted set may then be searched more exhaustively to improve the objective function. They differ from active-set methods in that the set of active constraints can change dramatically on each iteration, and they often exhibit stronger practical convergence behaviour, more akin to those of interior-point methods. However they rely heavily on projection, and thus are only suited to simple constraint geometries such as boxes and simplices.
